\cert{ Agbovi Eugene }{ Aggrey Memorial SHS }
\cert{ Theophilus Nyarko }{ Aggrey Memorial SHS }
\cert{ Nenyo - Jenkins Jehoiada }{ Aggrey Memorial SHS }
\cert{ Richard Mensah }{ Aggrey Memorial SHS }
\cert{ Adjei Jeffery }{ Aggrey Memorial SHS }
\cert{  Mantey Sene Fredrick }{ Aggrey Memorial SHS }
\cert{ Lawson Buabassah }{ Aggrey Memorial SHS }
\cert{ Abiwu Maxwell }{ Aggrey Memorial SHS }
\cert{ Frimpong Amoako David }{ Aggrey Memorial SHS }
\cert{ Quayson Fosuhene Michael }{ Aggrey Memorial SHS }
\cert{ Mawusi Gli Benedicta }{ St. Mary’s Senior High School }
\cert{ Liesi Akuokor Adjei }{ St. Mary’s Senior High School }
\cert{ Favour Okonkwo }{ St. Mary’s Senior High School }
\cert{ Maame Araba A. Sackey }{ St. Mary’s Senior High School }
\cert{ Joelle Eghan }{ St. Mary’s Senior High School }
\cert{ Dorothy Appiah-Adjei }{ St. Mary’s Senior High School }
\cert{ Gbedor-Kove Selasi }{ St. Mary’s Senior High School }
\cert{ Princess Ijeoma Oforji }{ St. Mary’s Senior High School }
\cert{ Kusi amponsah Takyiwaa Eunice  }{ St. Mary’s Senior High School }
\cert{ Maria Jochebed Duku }{ St. Mary’s Senior High School }
\cert{ Kezia Kwapong }{ St. Mary’s Senior High School }
\cert{ Rukaya Abubakar }{ St. Mary’s Senior High School }
\cert{ Salma Yusif }{ St. Mary’s Senior High School }
\cert{ Amposah Abigail }{ St. Mary’s Senior High School }
\cert{ Naomi Dacosta }{ St. Mary’s Senior High School }
\cert{ Carriesto Gyimah }{ Las Liberty School }
\cert{ Pia }{ Las Liberty School }
\cert{ Chidera }{ Las Liberty School }
\cert{ Ethel }{ Las Liberty School }
\cert{ Worlayram Vasmark-Voeborl }{ Las Liberty School }
\cert{ Abdul Aziz Baldeh }{ Las Liberty School }
\cert{ Cyril }{ Las Liberty School }
\cert{ Tommy }{ Las Liberty School }
\cert{ Jason }{ Las Liberty School }
\cert{ Chunanu }{ Las Liberty School }
\cert{ Kwame Oti-Mensah }{ Las Liberty School }
\cert{ Gerald Quaye-Kumah }{ Las Liberty School }
\cert{ Kaleb Ampromfi }{ Las Liberty School }
\cert{ Samuel Quaye }{ Las Liberty School }
\cert{ William Manirakiza }{ Las Liberty School }
\cert{ Enornam vasmark-Voegborlo }{ Las Liberty School }
\cert{ Charles Nnuro }{ Las Liberty School }
\cert{ Asare Kwabena Poku }{ Adisadel College }
\cert{ Dzathor Lee Eyram Caleb }{ Adisadel College }
\cert{ Opoku Elvis }{ Adisadel College }
\cert{ McEwan-Anamoah Cecil }{ Adisadel College }
\cert{ Anane Padmore Pius }{ Adisadel College }
\cert{ Asare Gideon Amoako Ohene }{ Adisadel College }
\cert{ Nud Billa  }{ Adisadel College }
\cert{ Karma Ahmed }{ Adisadel College }
\cert{ Obed Aforrisem }{ Adisadel College }
\cert{ Sekyi-Djan Kwabena }{ Adisadel College }
\cert{ Richmond Sefa Boateng  }{ Adisadel College }
\cert{ Dika Dennett Mawulolo }{ Adisadel College }
\cert{ Gyenin Paul }{ Adisadel College }
\cert{ Addison Kobina Ankomah }{ Adisadel College }
\cert{ Haleen Puumaya }{ Adisadel College }
\cert{ Agbe Sefordzi Gameli }{ Adisadel College }
\cert{ Dominic Kwame Blay }{ Adisadel College }
\cert{ Akoto Bismark }{ Achimota School }
\cert{ Ankrah Vince Churchhill }{ Achimota School }
\cert{ Bartz-Minlah Nkrumah Philip }{ Achimota School }
\cert{ Amoah-Bamfor Chrysol }{ Achimota School }
\cert{ Aya Lawrencia  }{ Achimota School }
\cert{ Enuwah Felila }{ Achimota School }
\cert{ Olanrewaju Michaeel }{ Achimota School }
\cert{ Deku Bradley Elikem }{ Achimota School }
\cert{ Arik Linah }{ Achimota School }
\cert{ Oddly Ethel Ayorkor }{ Achimota School }
\cert{ Ignatius A. Nanortey }{ Achimota School }
\cert{ Germain Dawson-Otoo }{ Achimota School }
\cert{ Apeakorang Vera }{ Achimota School }
\cert{ Mate Pace Kwesi Narh }{ Achimota School }
\cert{ Akpabie Eunice Jessica Adole }{ Achimota School }
\cert{ George Myron Freddy Othriel }{ Achimota School }
\cert{ Abdul-Aziz Najmuddeen }{ Achimota School }
\cert{ Objdqai Nii Sai Samuel }{ Achimota School }
\cert{ Samuel Boahene Yeboah }{ Achimota School }
\cert{ Geoffrey Ambele }{ The Roman Ridge School }
\cert{ Aseda Mills-Robenson }{ The Roman Ridge School }
\cert{ William Wedam Azemba  }{ The Roman Ridge School }
\cert{ King  David M Achampong }{ The Roman Ridge School }
\cert{ Nikita Ahuja }{ The Roman Ridge School }
\cert{ Tunishka Karnik }{ The Roman Ridge School }
\cert{ Malik Aryee-Boi }{ The Roman Ridge School }
\cert{ Goutham Kumar }{ The Roman Ridge School }
\cert{ Ghana Agha }{ The Roman Ridge School }
\cert{ Raphael Martinez-Aidoo }{ The Roman Ridge School }
\cert{ Oteng Lilian }{ University Practice SHS }
\cert{ Adasi -Appiah Christalene }{ University Practice SHS }
\cert{ Adani-Appiah Christabel }{ University Practice SHS }
\cert{ Kosivi Thelma Sedem }{ University Practice SHS }
\cert{ Kwansema Judene Nhyita Akua }{ University Practice SHS }
\cert{ Omaboe Abigail Norkor }{ University Practice SHS }
\cert{ Yushawu Mariam }{ University Practice SHS }
\cert{ Agyekum Joyce Walter }{ University Practice SHS }
\cert{ Antwi Victoria }{ University Practice SHS }
\cert{ Eshun Abigail }{ University Practice SHS }
\cert{ Davis Dallin }{ University Practice SHS }
\cert{ Baffour Sofo Arafat }{ University Practice SHS }
\cert{ Oppong- Boadi Benedicta  }{ University Practice SHS }
\cert{ Arkoh Frederick }{ University Practice SHS }
\cert{ Coffie Flint }{ University Practice SHS }
\cert{ Nti Johnson De-Graft }{ University Practice SHS }
\cert{ Jonathan J. Valentine  }{ University Practice SHS }
\cert{ Adom-Ampadu Martin }{ St. Thomas Aquinas SHS }
\cert{ Hammond Michael }{ St. Thomas Aquinas SHS }
\cert{ Ahumah Leslie Korda }{ St. Thomas Aquinas SHS }
\cert{ Abbey Nii Joshua  }{ St. Thomas Aquinas SHS }
\cert{ Davordzie -Banini Daniel David }{ St. Thomas Aquinas SHS }
\cert{ Woanya Sedem Raymond Prince }{ St. Thomas Aquinas SHS }
\cert{ Yeboah Osei }{ St. Thomas Aquinas SHS }
\cert{ Amoah Daniel Kwabena  }{ St. Thomas Aquinas SHS }
\cert{ Agbesi Clement Kobbyson }{ St. Thomas Aquinas SHS }
\cert{ Amanquah Leonard  }{ St. Thomas Aquinas SHS }
\cert{ Okay Conrad }{ St. Thomas Aquinas SHS }
\cert{ Davis Tettey Duordoe }{ St. Thomas Aquinas SHS }
\cert{ Grant Benjamin }{ St. Thomas Aquinas SHS }
\cert{ Nyadu Daniel }{ St. Thomas Aquinas SHS }
\cert{ Darko Philip }{ St. Thomas Aquinas SHS }
\cert{ Owusu Frank  }{ St. Thomas Aquinas SHS }
\cert{ Dampson Kelvin Kwadwo  }{ West African Senior High }
\cert{ Raphael Ndubuisi Daniel  }{ West African Senior High }
\cert{ Michael Boadu Mintah }{ West African Senior High }
\cert{ Asamoah Kumi Enoch }{ West African Senior High }
\cert{ Amimu Abdul Aziz Akondor }{ West African Senior High }
\cert{ Abraham Vincet }{ West African Senior High }
\cert{ Quansah Evans Kofi }{ West African Senior High }
\cert{ Baah Francis Later }{ West African Senior High }
\cert{ Tamakloe Awordews }{ West African Senior High }
\cert{ Kluise Gabriel }{ West African Senior High }
\cert{ Add Martin }{ West African Senior High }
\cert{ Foli Sarah }{ West African Senior High }
\cert{ Bright Dela Alidigah }{ West African Senior High }
\cert{ Fia Alfred  }{ Mfantsipim School }
\cert{ Salifu Mabruk Zelgene }{ Mfantsipim School }
\cert{ Jeffery Japhet Twumasi Owusu }{ Mfantsipim School }
\cert{ Adako Prince  }{ Mfantsipim School }
\cert{ Eshun Isaac Ekow }{ Mfantsipim School }
\cert{ Doccuvi Papa Kwame  }{ Mfantsipim School }
\cert{ Attipoe Steven Elorm }{ Mfantsipim School }
\cert{ Dadzie-Paintsil William Epaphras }{ Mfantsipim School }
\cert{ Hagan Ohenana Kyo Takyi }{ Mfantsipim School }
\cert{ Toffah Ato Kwamena Arko }{ Mfantsipim School }
\cert{ Ocloo Leonard Selasie }{ Labone Senior High School }
\cert{ George Quarshie Klenam }{ Labone Senior High School }
\cert{ Isaac Klutse }{ Labone Senior High School }
\cert{ David Jabez Dowuona }{ Labone Senior High School }
\cert{ Selorm Xortor }{ Labone Senior High School }
\cert{ Davida Dzato }{ Labone Senior High School }
\cert{ Kathy Awartey }{ Labone Senior High School }
\cert{ Benedicta Kudzordzi }{ Labone Senior High School }
\cert{ Enoch Gaglo }{ Labone Senior High School }
\cert{ Amoah Michael Sarfo }{ Labone Senior High School }
\cert{ Robert Amuzu Kwaku }{ Labone Senior High School }
\cert{ Daniel Nii Addotey Allotey }{ Labone Senior High School }
\cert{ Gbetey Sylvanus }{ Labone Senior High School }
